---
title: "papercheck"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{papercheck}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


## Installation

You can install the development version of papercheck from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("scienceverse/papercheck")
```

```{r}
library(papercheck)
```


### Load from XML

The function `read_grobid()` can read XML files in [TEI](https://tei-c.org/) format created by [grobid](https://grobid.readthedocs.io/). 

The example below uses some previously created XML files that are included with papercheck. You can [use grobid on your own paper](https://huggingface.co/spaces/kermitt2/grobid) here.

```{r}
grobid_dir <- system.file("grobid", package="papercheck")
filename <- file.path(grobid_dir, "incest.xml")
s <- read_grobid(filename)
```

## Full Text

You can access a parsed table of the full text of the paper via `s$full_text`, but you may find it more convenient to use the function `search_text()`. The defaults return a data table of each sentence, with the section type, header, div, paragraph and sentence numbers, and file name. (The section type is a best guess from the headers, so may not always be accurate.)

```{r}
text <- search_text(s)
```

```{r, echo = FALSE}
dplyr::filter(text, p == 1, s == 1) |>
  knitr::kable()
```

### Pattern

You can search for a specific word or phrase by setting the `pattern` argument. The pattern is a regex string by default; set `fixed = TRUE` if you want to find exact text matches.

```{r}
text <- search_text(s, pattern = "signific")
```

```{r, echo = FALSE}
knitr::kable(text)
```

### Section

Set `section` to a vector of the sections to search in.

```{r}
text <- search_text(s, "signific", 
                    section = "results")
```

```{r, echo = FALSE}
knitr::kable(text)
```


### Return

Set `return` to one of "sentence", "paragraph", "section", or "match" to control what gets returned.

```{r}
text <- search_text(s, "signific", 
                    section = "results", 
                    return = "paragraph")
```

```{r, echo = FALSE}
knitr::kable(text)
```

### Regex matches

You can also return just the matched text from a regex search by setting `return = "match"`. The extra `...` arguments in `search_text()` are passed to `grep()`, so `perl = TRUE` allows you to use more complex regex, like below.

```{r}
pattern <- "[^\\s\\(\\)]+\\s*(=|<)\\s*[0-9\\.-]+"
text <- search_text(s, pattern, return = "match", perl = TRUE)
```

```{r, echo = FALSE}
knitr::kable(text)
```


## Batch Processing

The function `read_grobid()` also works on a folder of XML files, returning a list of scienceverse study objects, and `search_text()` works on such a list.

```{r}
studies <- read_grobid(grobid_dir)

hypotheses <- search_text(studies, "hypothesi", 
                          section = "intro", 
                          return = "paragraph")
```


## ChatGPT

You can query the extracted text of papers with chatGPT.

### Setup

You will need to provide your own [API key](https://platform.openai.com/api-keys). You can enter it manually for each call to `gpt()`, or add the following line in the .Renviron file for your user or project. 


``` bash
CHATGPT_KEY="sk-proj-abcdefghijklmnopqrs0123456789ABCDEFGHIJKLMNOPQRS"
```

```{r, eval=FALSE}
# useful if you aren't sure where this file is
usethis::edit_r_environ()
```

### GPT Queries

```{r, eval = FALSE}
query <- "What is the hypothesis of this study?"
gpt_hypo <- gpt(hypotheses, query)
```

```{r, echo = FALSE}
gpt_hypo <- structure(list(file = c("eyecolor.xml", "incest.xml", "prereg.xml"
), answer = c("The hypothesis of this study is to test the matching hypothesis, sex-linked heritable preference hypothesis, and positive sexual imprinting hypothesis in relation to eye color and partner selection.", 
"The hypothesis of this study is that humans possess adaptations to reduce inbreeding, and that the strong moral opposition to incest plays an important role in preventing inbreeding.", 
"The hypothesis of this study is that more efficient study designs might increase the willingness to pre-register in psychological science."
), cost = c(0.000612, 0.000216, 0.000608)), row.names = c(NA, 
-3L), class = c("tbl_df", "tbl", "data.frame"))
knitr::kable(gpt_hypo)
```



