---
title: "papercheck"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{papercheck}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(papercheck)
```

## Load from XML

The function `read_grobid()` can read XML files in [TEI](https://tei-c.org/) format created by [grobid](https://grobid.readthedocs.io/). 

```{r}
grobid_dir <- system.file("grobid", package="papercheck")
filename <- file.path(grobid_dir, "incest.xml")
s <- read_grobid(filename)
```

## Full Text

You can access a parsed table of the full text of the paper via `s$full_text`

```{r}
dplyr::count(s$full_text, section)
```

However, you may find it more convenient to use the function `search_text()`.

```{r}
sig <- search_text(s, "signific")

sig$text
```

You can also return just the matched text from a regex search.

```{r}
pattern <- "[^\\s\\(\\)]+\\s*(=|<)\\s*[0-9\\.-]+"
search_text(s, pattern, section = "results", return = "match", perl = TRUE)
```


## Batch Processing

The function `read_grobid()` also works on a folder of XML files, returning a list of scienceverse study objects, and `search_text()` works on such a list.

```{r}
studies <- read_grobid(grobid_dir)

hypotheses <- search_text(studies, "hypothesi", section = "intro")

hypotheses$text
```

